|

### 2020-10-21 paper/v1/broadband.speed.covid.Rmd
juut brought some of the google doc text

**PARA1**: working from home is a challenge and maybe an opportunity [use arguments from @BUDNITZ2020102713]
It has been altered dramatically because of covid

>>>>

<!-- **PARA1**: working from home is a challenge and maybe an opportunity [use arguments from @BUDNITZ2020102713] -->
<!-- It has been altered dramatically because of covid -->

During the pandemic, working from home using Information and Communication
Technologies (ICT), whether partially or exclusively, was transformed from a
niche means of accessing work, albeit one that had been on a slow, upward trend,
to a widespread way of life in many countries.
The ability to work from home or telecommute meant millions retained their jobs
and, to a varying extent, maintained productivity during periods of strict
lockdown around the world.
However, this ability was not evenly distributed socially or spatially, creating
a new type of digital divide -- one of economic resilience and personal safety on
one side and unemployment or essential front-line work on the other.
The ability to telecommute is partly a product of whether the majority of work
tasks in an occupation can be performed independently of being in a particular
location or co-locating with colleagues.
It is also a product of the quality of ICT services, particularly home internet
connections, sufficient to successfully complete work tasks with a minimum of
delay or interruption.
Therefore, in this paper, we aim to look at patterns of broadband speed tests
and upload speeds in the UK in order to gain insights into both the quality and
reliability of broadband services across the country and the distribution of
telecommuting at the time when the population were told to work from home if
possible.
From this analysis, we provide a greater understanding of how telecommuting and
technology intersect at a time of extreme demand, and what lessons this time has
for a future where telecommuting is likely to remain a common means of accessing
work and broadband services, as well as infrastructure, must be fit for purpose.
